Deep Reinforcement Learning for Conservation Decisions

### 2022-07-05 manuscript/manuscript.Rmd
Changing names in Contributions

All authors were supported by the NSF Faculty Early Career Development Program Award 1942280. We thank Benjamin Blonder, Zachary Sunberg, and Claire Tomlin for their thoughtful comments.

@@

M.L. and C.B. developed the code and wrote the manuscript with support from K.E.A.N. and M.S.C.

>>>>

This material is based upon work supported by the National Science Foundation under Grant No. DBI-1942280. We thank Benjamin Blonder, Zachary Sunberg, and Claire Tomlin for their thoughtful comments.

@@

Marcus Lapeyrolerie and Carl Boettiger developed the code and wrote the manuscript with support from Kari Norman and Melissa Chapman.
